\documentclass{article}
\usepackage[utf8]{inputenc}

\title{AMTE21 - Preface}
\author{Patrick Diehl}
\date{March 2021}

\begin{document}
\noindent The workshop Asynchronous Many-Task systems for Exascale (AMTE) 2021 was held at x in conjunction with 27th International European Conference on Parallel and Distributed Computing (EuroPar) as a virtual event. The goal of the workshop was to explore the advantages of task-based programming on modern and future high performance systems. It gathered developers, users, and proponents of these models and systems to share experiences, discuss how they meet the challenges posed by Exascale system architectures, and explore opportunities for increased performance, robustness, and full-system utilization.

The workshop was organized by Irina Demeshko, Patrick Diehl, Steven R. Brandt, Zahra Khatami, and Parsa Amini. The keynote was given by Thomas Fahringer and the invited talk by Daisy Hollman. The panel discussion was moderated by Irina Demeshko with the following panelists: Hartmut Kaiser, Laxmikant (Sanjay) Kale, Martin Berzins, Mike Bauer, and Thomas Fahringer.

This volume of LNCS compromises selected contributions of attendees of this event. The contributed papers range from optimization of asynchronous many-task runtime systems to applications. This workshop has shown that AMTs are widely used in academia and national laboratories, and researchers are working to address some challenges posed by Excascale system architectures.\\

\noindent
Baton Rouge,\hfill Patrick Diehl\\
Baton Rouge,\hfill Steven R. Brandt\\
Baton Rouge,\hfill Parsa Amini\\
Santa Clara,\hfill Zahra Khatami\\
New Mexico,\hfill Irina Demeshko\\
October 2021

\end{document}
