\documentclass{llncs}
\usepackage[utf8]{inputenc}

\begin{document}

% please remember the 2 pages maximum size for each workshop

\section*{Asynchronous Many-Task systems for Exascale (AMTE)}

\subsection*{Workshop Description}
The workshop, Asynchronous Many-Task systems for Exascale (AMTE) 2021, was held at x in conjunction with the 27th International European Conference on Parallel and Distributed Computing (EuroPar) as a virtual event. The goal of the workshop was to explore the advantages of task-based programming on modern and future high performance systems. It gathered developers, users, and proponents of these models and systems to share experiences, discuss how they meet the challenges posed by Exascale system architectures, and explore opportunities for increased performance, robustness, and full-system utilization.

The workshop was organized by Irina Demeshko, Patrick Diehl, Steven R. Brandt, Zahra Khatami, and Parsa Amini. The keynote was given by Thomas Fahringer, and the invited talk by Daisy Hollman. The panel discussion was moderated by Irina Demeshko with the following panelists: Hartmut Kaiser, Laxmikant (Sanjay) Kale, Martin Berzins, Mike Bauer, and Thomas Fahringer.

This volume of LNCS compromises selected contributions of attendees from this event. The contributed papers range from optimization of asynchronous many-task runtime systems to applications. This workshop has shown that AMTs are widely used in academia and national laboratories, and researchers are working to address some challenges posed by Excascale system architectures.


\subsection*{Steering Committee}
%Please introduce one name and affiliation per line as below.
\begin{tabular}{@{}p{5cm}@{}p{7.2cm}@{}}
Parsa Amini & Louisiana State University, USA\\
teven R. Brandt & Louisiana State University, USA\\
Irina Demeshko & Los Alamos National Laboratory, USA\\
Patrick Diehl & Louisiana State University, USA\\
Zahra Khatami & NVIDIA, USA\\
\end{tabular}


%\subsection*{Program Chair}
%In case of more than one char, please introduce one name and affiliation per line as below.
%\begin{tabular}{@{}p{5cm}@{}p{7.2cm}@{}}
%Loris Marchal & CNRS \& University of Lyon, France
%\end{tabular}

\subsection*{Program Committee}
%Please introduce one name and affiliation per line as below.
\begin{tabular}{@{}p{5cm}@{}p{7.2cm}@{}}
Didem Unat & Koç University, Turkey\\
Dirk Pleiter & Jülich Supercomputing Centre, Germany \\
Roman Lakymchuk & Fraunhofer ITWM, Germany \\
Vassilios Dimakopoulos & University of Ioannina, Greece \\
Thomas Heller & Exasol, Germany \\
Jeff Hammond & NVIDIA \\
Hartmut Kaiser & Center for Computation \& Technology at Louisiana State University, USA \\
Erwin Laure & Max Planck Computing \& Data Facility, Germany \\
Gregor Daiss & University of Stuttgart, Germany \\
Vassilios Dimakopoulos & University of Ioannina, Greece \\
Patricia Grubel & Los Alamos National Laboratory, USA \\
Jeff Hammond & NVIDIA, USA \\
Adrian Lemoine & AMD, USA \\
Mikael Simberg & Swiss National Supercomputing Centre, Switzerland \\
Laxmikant (Sanjay) V. Kale & University of Illinois at Urbana-Champaign, USA \\
Galen Shipman & Los Alamos National Laboratory, USA \\
Brad Richardson & Sourcery Institute, USA \\
Shahrzad Shirzad & Center for Computation \& Technology at Louisiana State University, USA \\
Nanmia Wu & Center for Computation \& Technology at Louisiana State University, USA \\
Kevin Huck & University of Oregon, USA \\
Andrew Lumsdaine & University of Washington; Pacific Northwest National Laboratory, USA \\
H. Metin Aktulga & MSU College of Engineering, USA
\end{tabular}

\end{document}